\texttt{ensmallen}: a generic C++ library for fast optimization

### 2018-10-14 doc/mlsys_paper/paper.tex

\begin{abstract}
% TODO: not sure this is a great abstract
ensmallen is cool software and you should use it.
\end{abstract}

>>>>

\begin{abstract}

%% the abstract below still needs more meat and sharpening

We present a fast and flexible C++ library for mathematical optimization of 
arbitrary user-supplied functions,
which can be applied to many machine learning problems.
The library provides many pre-built optimizers
(including numerous variants of SGD and Quasi-Newton optimizers)
as well as a flexible framework for implementing new optimizers and objective functions.
Implementation of a new optimizer requires only one method
and implementation of a new objective function requires at most four C++ functions. 
This can aid in the  quick implementation and prototyping of new machine learning algorithms.
In contrast to optimization approaches in existing frameworks
(such as Julia, Shogun, Vowpal Wabbit, SciPy),
the proposed Ensmallen library supports more optimizations,
more types of objective functions,
as well as seamlessly supporting user-defined objective functions and optimizers.
Empirical comparisons show that ...
TODO: briefly describe the speedups obtained in the experiments

\end{abstract}
